### 2018-05-29 submission/manuscript.Rmd
redo final section of results

***Prevalence of Chimeric Sequences are Polymerase Dependent and Correlate with the Number of OTUs:***  Based on the previous results, we examined whether chimeras also were dependent on polymerase and whether this could affect the number of OTUs. 
There is significant differences in the chimera prevalence based on polymerase at all the number of cycles used (P-value `r ifelse(max(filter(kruskal_chimera_prev)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S3]. Differences in chimera prevalence between Platinum and all other polymerases accounted for the majority of these differences [Table S4]. Accuprime^TM^ had the lowest chimera prevalence of all polymerases regardless of whether chimera removal with VSEARCH was used [Figure 5A & 5B]. Additionally, there was a plateau in the total percent of chimeras that were removed that was similar for all polymerases [Figure 5C]. A positive correlation was observed between chimeric sequences and the number of OTUs for all polymerases [Figure 6]. This positive correlation was strongest for Accuprime^TM^, Platinum, and Phusion [Figure 6]. This data suggests that chimera prevalence depends on polymerase used and confirms that the number of OTUs is dependent on the prevalence of these chimeric sequences.

>>>>

***Prevalence of chimeric sequences are polymerase dependent and correlate with the number of OTUs:***  Based on the previous results, we examined whether chimeras also were dependent on polymerase and whether this could affect the number of OTUs. We observed significant differences in the chimera prevalence based on polymerase across the number of cycles used (P-value `r ifelse(max(filter(kruskal_chimera_prev)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S3]. Differences in chimera prevalence between Platinum and all other polymerases accounted for the majority of these differences [Table S4]. Accuprime^TM^ had the lowest chimera prevalence of all polymerases regardless of whether chimera removal with VSEARCH was used [Figure 5A & 5B]. The number of cycles used clearly increased chimera prevalence for all polymerases but the rate of increase differed [Figure 5A & 5B]. Additionally, there was a plateau in the total percent of chimeras that were removed that was similar for all polymerases [Figure 5C]. A positive correlation was observed between chimeric sequences and the number of OTUs for all polymerases [Figure 6]. This positive correlation was strongest for Accuprime^TM^, Platinum, and Phusion [Figure 6]. This data suggests that chimera prevalence depends on polymerase, is made worse by increasing the number of cycles, and confirms that the number of OTUs is dependent on the prevalence of these chimeric sequences.

### 2018-05-29 submission/manuscript.tex
redo final section of results

\textbf{\emph{Prevalence of Chimeric Sequences are Polymerase Dependent
and Correlate with the Number of OTUs:}} Based on the previous results,
we examined whether chimeras also were dependent on polymerase and
whether this could affect the number of OTUs. There is significant
differences in the chimera prevalence based on polymerase at all the
number of cycles used (P-value \textless{} 0.05) {[}Table S3{]}.
Differences in chimera prevalence between Platinum and all other
polymerases accounted for the majority of these differences {[}Table
S4{]}. Accuprime\textsuperscript{TM} had the lowest chimera prevalence
of all polymerases regardless of whether chimera removal with VSEARCH
was used {[}Figure 5A \& 5B{]}. Additionally, there was a plateau in the
total percent of chimeras that were removed that was similar for all
polymerases {[}Figure 5C{]}. A positive correlation was observed between
chimeric sequences and the number of OTUs for all polymerases {[}Figure
6{]}. This positive correlation was strongest for
Accuprime\textsuperscript{TM}, Platinum, and Phusion {[}Figure 6{]}.
This data suggests that chimera prevalence depends on polymerase used
and confirms that the number of OTUs is dependent on the prevalence of
these chimeric sequences.

>>>>

\textbf{\emph{Prevalence of chimeric sequences are polymerase dependent
and correlate with the number of OTUs:}} Based on the previous results,
we examined whether chimeras also were dependent on polymerase and
whether this could affect the number of OTUs. We observed significant
differences in the chimera prevalence based on polymerase across the
number of cycles used (P-value \textless{} 0.05) {[}Table S3{]}.
Differences in chimera prevalence between Platinum and all other
polymerases accounted for the majority of these differences {[}Table
S4{]}. Accuprime\textsuperscript{TM} had the lowest chimera prevalence
of all polymerases regardless of whether chimera removal with VSEARCH
was used {[}Figure 5A \& 5B{]}. The number of cycles used clearly
increased chimera prevalence for all polymerases but the rate of
increase differed {[}Figure 5A \& 5B{]}. Additionally, there was a
plateau in the total percent of chimeras that were removed that was
similar for all polymerases {[}Figure 5C{]}. A positive correlation was
observed between chimeric sequences and the number of OTUs for all
polymerases {[}Figure 6{]}. This positive correlation was strongest for
Accuprime\textsuperscript{TM}, Platinum, and Phusion {[}Figure 6{]}.
This data suggests that chimera prevalence depends on polymerase, is
made worse by increasing the number of cycles, and confirms that the
number of OTUs is dependent on the prevalence of these chimeric
sequences.
